\section*{Problem A. Are the Nodes Reachable?}
Problem Setter: Raihat Zaman Neloy\\
Tester: Rumman Mahmud, Pritom Kundu, Nafis Sadique\\
Cetegory: Ad-hoc\\
Total Solved: \\
First to Solve: \\
\\
We can split the problem is two subproblem.
\paragraph*{When $ans < 32$.}
How do we solve it? First for each vertex calculate the list of vertex reachable from it. Also
calculate the list of vertex from which it is reachable. Both can be done in $O(\frac{max(n) \cdot m}{64})$ using bitsets.
Now assume that vertex $a$ is reachable from vertex $b$. In that case vertices $b-1$ or $b+1$ will be reachable by 
adding an edge of cost 1. We can find all the vertices from which vertex $a$ is reachable with 1 cost by simply
binary shifting the bitset by 1 in both direction and apply the bitwise OR operator on all three (no change, left shift, right shift).
If we do this again then we find the vertices 2 distance away and so on. We keep doing this for distances upto 31. The
complexity to do this is $O(\frac{n^2*32}{64})$. 
\\
\\
Now, lets split the bitsets into $64$ sized buckets. Technically we could've used an unsigned long long array to perform
the bitset operations in the first place. For each vertex we will have 33 bitset buckets. 32 of them are for
the shifted bitsets from upstream and one for the downstream.
Then for the query, we check if the first upstream bucket of V with 31 shift and the downstream bucket of U has any match. We 
can do that by simply performing a bitwise AND operation. If there is a match then we check 30 shift and keep reducing it. If 
no match is found then we move to the next bucket. At the end in this approach we will need $O(\frac{n}{64}+32)$ operations
per query.
\paragraph*{When $ans \ge 32$.}
We again keep a bucket of vertices reachable from a vertex. Vertices numbered from [1..64] are in one bucket, [65, 128] are 
in second buckets and so on. For each bucket we only keep the minimum and maximum id of the vertex reachable from it. Similarly we do it 
for the upstream vertices. For a query, we merge those two list of vertices (min and max of each bucket), sort them and find the
smallest gap in consecutive vertices (one must be upstream while the other must be downstream). This takes $O(\frac{n*2}{64})$ per
query.
\\ 
\\
Alternatively, we can do the same using 128 bit integers. The performance is comparable.
